---
title: "Correlation Turkuflats"
output: html_notebook
---

Read in the output from the "cleaning" Python script.

```{r}
library(tidyverse)
library(GGally)



```
```{r}

flats <- read.csv('/home/chpatola/Desktop/Skola/Python/turku_flatprices/data/pre-processed/processedFlats.csv') %>% 
  glimpse()

```
```{r}
dim(flats)
```


We see few surprises in the correlations. Built year is clearly correlated with energy class

```{r}
ggpairs(flats[,c(2:7,40)])
```               
```{r}
pca_flats <- prcomp(flats)
summary(pca_flats)

biplot(pca_flats, choices = 1:2, col=c("black","blue"))
```
All variation can be explained by the first principal component



```{r}
pairs(flats[,2:7])

```
Let's try linear regression

```{r}
fit <- lm(y ~ .,data=flats) 
summary(fit)
```



Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
